### 2021-03-25 README.Rmd
FIX BRANCH TO 'main' IN BINDER LINK

<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/jmlondon/berchukHaulout/master?urlpath=rstudio)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Launch Rstudio Binder](http://mybinder.org/badge_logo.svg)](https://mybinder.org/v2/gh/jmlondon/berchukHaulout/main?urlpath=rstudio)
<!-- badges: end -->
